AA Distributed Software Development Methodology

### 2013-02-18 paper.tex
3rd and 4rth par improved

However, dispite the advantages of GCD, we have noticed how
difficult it is to coordinate and fund free software on a larger scale
than currently available, when teams are very heterogeneous containing
not only volunteers and very experienced developers, but also
contractors from different backgrounds and cultures. Our observations
found base on the factors suggested by Carmel~\cite{carmel1999} as
main difficulties for GCD: distance, time and cultural differences. In
the case of free or open software projects, all these factors are
involved.

Another problem faced by modern software companies and other
collectives are frequent ineffective meetings, which are seldom
focused to the interest to any attendant. The result is that it has
become the norm to participate in too many meetings with the ``laptop
open'', which is unproductive at the very least. Software developers
like to code, to be productive, to have their hands on their project,
to do what they are best at. They dislike to have to stop for meetings
or to write lengthy reports to justify their funding.
%\todo{ler mais. cacm, etc}

Here we propose AA, a methodology and an associated software system
for coordinating distributed team work dealing with the disadvantages
of GSD. Team members take on an egalitarian role, and stay
voluntarily \textit{logged} in the system for part of their time
(e.g.\ 2 hours per day), during which they log a periodical short text
sentence --- similar to a ``tweet'' in this Twitter era --- as the
status of their activity using an easy to use command. These
``microblog sentences'' are publicly aggregated and validated by other
team members. Through AA, we have a methodology and an associated
system to validate and enable the activities of a distributed software
team. It implicitly legitimizes financial support for the expansion of
the activity of the developer team. The AA methodology is specially
useful for coordinating distributed and decentralized team work,
providing effective means to asynchronously update different team
members without the need for synchronous unproductive meetings.

>>>>

Despite the advantages of GCD, we have noticed how
difficult it is to coordinate and fund free software on a larger scale
than currently available, when teams are very heterogeneous containing
not only volunteers and very experienced developers, but also
contractors and freelancers from different backgrounds and cultures. Our observations
are founded on the factors suggested by Carmel~\cite{carmel1999} as
main difficulties for GCD: distance, time and cultural differences. In
the case of free or open software projects, all these factors are
involved.

Another problem faced by modern software companies and other
collectives are frequent ineffective meetings, which are seldom
focused to the interest to any attendant. The result is that it has
become the norm to participate in too many meetings with the ``laptop
open'', which can be un-productive. Software developers
like to code, to be productive, to have their hands on their project,
to do what they are best at. They dislike to forcibly stop for meetings
or to do other bureaucratic activities such as writing lengthy reports to justify their funding.
%\todo{ler mais. cacm, etc}

In this paper we propose the AA methodology and an associated software system
for coordinating distributed team work, tackling the disadvantages
of GSD. Team members take on an egalitarian role, and stay
voluntarily \textit{logged} in the system for part of their time
(e.g.\ 2 hours per day), during which they log a periodical short text
sentence --- similar to a ``tweet'' in this Twitter era --- as the
status of their activity using an easy to use command. These
``microblog sentences'' are publicly aggregated and validated by other
team members. Through AA, we have a methodology and an associated
system to validate and enable the activities of a distributed software
team. It implicitly legitimizes financial support for the expansion of
the activity of the developer team. The AA methodology is specially
useful for coordinating distributed and decentralized team work,
providing effective means to asynchronously update different team
members without the need for synchronous unproductive meetings.
